Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-06-07 supp_theo_specs.tex
work on supporting information

\subsection{Clusters with $N=38$ Atoms of Different Composition}
Recently, structures for ArXe clusters of in total 38 atoms were optimized
using an evolutionary algorithm based on two-body potentials of the Lennard-Jones (LJ) type, or using two other models aimed at improving over the simple LJ potential.\cite{marques}
In this section, the simulated ICD and ETMD(3) spectra for selected cluster
structures shown in Figure 7 of Ref. \citenum{marques} are shown in Figures
\ref{figure:ArXe_lt15} -- \ref{figure:ArXe_gt50} and discussed.

>>>>

\subsection{Clusters with $N=38$ Atoms of Different Composition}
Recently, structures for ArXe clusters of in total 38 atoms were optimized
using an evolutionary algorithm based on two-body potentials of the
Lennard-Jones (LJ) or the improved Lennard-Jones type \cite{marques,Pirani08},
which have been fitted to experimental parameters.
In this section, the simulated ICD and ETMD(3) spectra for selected cluster
structures shown in Figure 7 of Ref. \citenum{marques} are shown in Figures
\ref{figure:ArXe_lt15} -- \ref{figure:ArXe_gt50} and discussed.
